Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2021-09-03 vertical-thermal-review_SI.Rmd
a bit oof cleanup, added TOC

---
title: 'Supporting Information'
output: word_document
bibliography: Zotero_references.bib
csl: new-phytologist.csl

@@

**Title:** Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

**Authors:** 
Nidhi Vinod^1^,
Martijn Slot^2^,
Ian McGregor^3^,
Elsa M. Ordway^4^,
Marielle N. Smith^5^,
Tyeen Taylor,
Lawren Sack,
Kristina J. Anderson-Teixeira^1,2^*

@@

S1 Note:

It is noteworthy that leaf and branch temperatures often differ substantially. For instance, exposed tropical tree bark can be much warmer than leaves [@pauTropicalForestTemperature2018; @stillImagingCanopyTemperature2021; @johnstonWhatLiesVertical2020]. 
Thus, vegetation temperature ($T_{veg}$) measured using sensors that integrate across both leaves and woody vegetation (e.g., infrared sensors for $T_{veg}$ at NEON sites, Fig. `r fig_NEON_vertical`h) does not always equal $T_{leaf}$, particularly in settings where leaf area is low relative to woody vegetation (*i.e.*, low-LAI ecosystems and understories). 
Recent advances in $T_{leaf}$ modeling (see "Scaling across Space and Time") will enhance our understanding of large scale $T_{leaf}$ vertical patterns [@stillImagingCanopyTemperature2021; @macleanMicroclimcMechanisticModel2021]

>>>>

---
title: 'Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications'
output:
  word_document:
    toc: true
    toc_depth: 2
bibliography: Zotero_references.bib
csl: new-phytologist.csl

@@

@@
